### 2014-06-01 ACL2014/system.tex
Update system.tex

\section{Problem Statement}
We start with user query logs \corpus having query vectors collected from 
a commercial search engines over some domain (e.g. URLs); similarity between queries is to be measured using cosine between the corresponding
vectors. 
The problem we formulate here is given a set of queries $Q$ and similarity threshold $\tau$,
we are interested in developing a batch process to return a \emph{small}
set $T$ of candidate neighbors from \corpus for each query $q \in Q$ such that the followings
are satisfied: 1) $T = \{ l \mid s(l, q) \geq \tau,  l \in C  \}$, where  $s(q_1, q_2)$ is a function to
compute a similarity score between query $q_1$ and $q_2$
; 2) $T$ achieves $100\%$ precision with ``large'' recall. 
That is, our aim is to achieve a large recall, while using
a scalable efficient algorithm.

>>>>

\section{Problem Statement}
We start with user query logs \corpus having query vectors collected from 
a commercial search engines over some domain (e.g. URLs); similarity between queries is to be measured using cosine between the corresponding
vectors. 
The problem we formulate here is given a set of queries $Q$ and similarity threshold $\tau$,
we are interested in developing a batch process to return a \emph{small}
set $T$ of candidate neighbors from \corpus for each query $q \in Q$ such that the followings
are satisfied: 1) $T = \{ l \mid s(l, q) \geq \tau,  l \in C  \}$, where  $s(q_1, q_2)$ is a function to
compute a similarity score between query feature vector $q_1$ and $q_2$
; 2) $T$ achieves $100\%$ precision with ``large'' recall. 
That is, our aim is to achieve a large recall, while using
a scalable efficient algorithm.
